---
title: "ideal Users Guide"
author: "**Federico Marini** (marinif@uni-mainz.de) and **Harald Binder**</br>
  Institute of Medical Biostatistics, Epidemiology and Informatics (IMBEI), Mainz </br>
  Center for Thrombosis and Hemostasis (CTH), Mainz"
email: marinif@uni-mainz.de  
date: "`r doc_date()`"
package: "`r pkg_ver('ideal')`"
abstract: >
  `r Biocpkg("ideal")` provides functionality for interactive visualization of RNA-seq datasets
  based on Principal Components Analysis. Such methods allow for quick information 
  extraction and effective data exploration. A Shiny application encapsulates the whole analysis, and
  is developed to become a practical companion for any RNA-seq dataset. This app supports reproducible
  research with state saving and automated report generation. 
output: 
  BiocStyle::html_document:
    fig_caption: TRUE
vignette: >
  %\VignetteIndexEntry{ideal Users Guide}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}  
  %\VignettePackage{ideal}
  %\VignetteKeywords{GeneExpression, DifferentialExpression, RNASeq, Sequencing, Visualization, QualityControl, GUI, GeneSetEnrichment, ReportWriting}
---

<br>
**Package**: `r Rpackage("pcaExplorer")`<br />
**Authors**: `r packageDescription("pcaExplorer")[["Author"]]`<br />
**Version**: `r packageDescription("pcaExplorer")$Version`<br />
**Compiled date**: `r Sys.Date()`<br />
**License**: `r packageDescription("pcaExplorer")[["License"]]`<br />

```{r style, echo = FALSE, results = 'asis'}
BiocStyle::markdown()
```

```{r setup, echo=FALSE, warning=FALSE}
library(knitr)
set.seed(42)
opts_chunk$set(comment=NA,
               fig.align="center",
               warning=FALSE)
```

# Getting started

`r Biocpkg("ideal")` is an R package distributed as part of the [Bioconductor](http://bioconductor.org) project. To install the package, start R and enter:

```{r installation, eval=FALSE}
source("http://bioconductor.org/biocLite.R")
biocLite("ideal")
```

If you prefer, you can install and use the development version, which can be retrieved via Github (https://github.com/federicomarini/ideal). To do so, use

```{r installation-github, eval=FALSE}
library("devtools")
install_github("federicomarini/ideal")
```



Once `r Rpackage("ideal")` is installed, it can be loaded by the following command.

```{r loadlibrary, message=FALSE}
library("ideal")
```

```{r}
sessionInfo()
# devtools::session_info()
```


